Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-06 main.tex
WIP on Discussion

\subsection{Cognitive Priming and Interaction Situation}

@@

The significant impact of the machine-like \vs human-like conditions on the
answers to the question \emph{Were the tasks more ``a robot kind of task'' or
``a human kind of task''?} shows that our manipulation was effective: framing
the interaction situation to induce a machine-like or a human-like task context
was successful.

situation priming the participants with , and that a machine-like cognitive
context was indeed perceived to elicit a ``robot-like'' situation, while a
human-like
cognitive priming was perceived as a ``human-like'' situation. This supports our
first hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
sufficient to elicit significantly increased attribution of human-likeness.

>>>>

\subsection{Cognitive Priming and Interaction Situation}
\label{cognitive-priming}

@@

The significant impact of the machine-like \vs human-like conditions on the
answers to the question \emph{Were the tasks more ``a robot kind of task'' or
``a human kind of task''?} shows that our manipulation was effective: framing
the interaction situation to induce a machine-like or a human-like task context
was successful. By further showing that the conditions also impact the
reported tendency to attribute anthropomorphic traits to robots in general (as assessed by
the Godspeed questionnaire), we conclude that our manipulation of the commands
given to the robot effectively influenced the participants in perceiving the
robot as anthropomorphic.

We interpret this result as the consequence of building in each condition a
different set of expectation regarding the cognitive skills of the robot: when a
participant hears the robot being instructed ``Pick up your favourite toy'', she
implicitly (and likely, unconsciously) supposes that the robot has the cognitive
capabilities required to \emph{prefer} one toy to another one, which would also
typically implies that the robot understand the affective dimensions of toys. By
performing this reasoning, the human would (likely unconsciously) attribute
cognitive and emotional traits to the robot that are akin to humans, and as a
result, anthropomorphise more the robot. Similarly for the command ``Point at
the crying baby'' that elicits not only emotional attributions related to cries
and babies, but also suggests that the robot has a sense of the urgency of
the situation (a baby is crying!). Our manipulation makes the robot appear as it
possesses a commonsense knowledge of a typically human situation.

Remarkably (and in line with the literature reviewed in
section~\ref{cognitive-priming}), these cognitive ascriptions lead to a visible
change in the participants' behaviour: they gaze more at the head of the robot
when they watch a scene that elicits stronger anthropomorphic attributions.
Several explanations can be thought of. At an abstract level, the head may
typically be seen as embodying the mind and the emotions. As such, the head of
an agent that is believed to be endowed with such cognitive and emotional
abilities could be thought to be of higher importance, attracting more
attention. Another explanation pertains to the social norms elicited by a moral
agent~\citep{malle2014moral}. We can reasonably suppose that a robot thought to
be endowed with rich cognitive skills is likely to be considered more as a moral
agent as a robot with an apparent mechanical behaviour. As a result, the
participant might be led to adhere to social norms (including looking at the
face when interacting) when watching the robot. A third explanation involves
automatic social behaviours: if the participant is tricked into believing that
the robot might have rich cognitive skills, she might automatically search for
even more socio-cognitive cues, and the face is a particularly rich source of
such cues (facial expressions, gaze, back-channel communication like nodding).
